### 2020-11-12 proposals/white-paper/white-paper.tex
latex syntax fixup
spacing on proposals reduced
table L update for raggedright
style fix
section mods for proposals

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
\newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell

@@

\noindent\textbf{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} We anticipate the following outcomes: (1), (2), (3), (4), (5), and (6) Identify lessons learned and engage in future pathways and partnerships.
\\

\noindent\textbf{Estimated Cost of the Project.} We request a total of \$X,XXX,XXX for this project for a timeframe of N years.
\\

>>>>

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
\newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell
\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}} %uses \raggedright with p{} in table column

%\paragraph and \subparagraph modifiers
% no indent for each
% after \z@ pads whitespace on the top
% em sets the distance after heading to text horizonally

\makeatletter
\renewcommand\paragraph{%
    \@startsection{paragraph}{4}{\z@ }{0.55\baselineskip}{-1em}
    {\normalfont \normalsize \bfseries}}%

\makeatletter
\renewcommand\subparagraph{%
    \@startsection{subparagraph}{5}{\z@ }{0.45\baselineskip}{-1em}
    {\normalfont \normalsize \itshape }}%

\makeatletter
\renewcommand\subsection{%
    \@startsection{subsection}{2}{\z@ }{0.75\baselineskip}{0.25\baselineskip}
    { \large \bfseries}}%

@@
